\begin{abstract}
With the remarkable advancement in computing and communications, e-commerce has become ubiquitous. Understanding customers in this space, especially their interest and purchase behavior, which are highly correlated with demographics, is crucial for organizations like Amazon. 
%Customer's interest and purchase pattern is believed to be highly correlated with her demographics. 
In general customers also buy for their family, friends and relatives. So knowing the household demographics is helpful in improving customer experience. In this work, our goal is to automatically discover the demographic composition of a household. 
%More specifically we intend to discover whether there is a member in the household with a specific age group.
More specifically we intend to discover whether there is a member of a specific age group (e.g., age between 25 and 35) present in the household.
%We considered six age groups: 18-24, 25-34, 35-44, 45-54, 55-64 and above 65.
%the age group of each member inside a household. 
There are multiple challenges involved: \textit{few discriminative purchases, noise in purchases and unavailability of clean labels} to build predictive models. We address these challenges by applying suitable multilabel classification algorithms including methods exploiting the label correlation. We discuss advantages and limitations of various approaches and present empirical results with insights from thoroughly designed experiments. We also investigate the feature and label noise in the data and provide explanations for our predictions that can help in taking business decisions. A variant of our approach predicts the account holder's age group and is currently being used by more than 20 teams inside Amazon.
\end{abstract}







